---
title: "Bayesian_Final Code"
author: "Dehua Bi"
date: "13/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproduce Blog Code

```{r}
library(Hmisc)
library(rms)

# Prior data
sd1 <- 1 / qnorm(1 - 0.1)
sd2 <- 0.25 / qnorm(1 - 0.05)
wt <- 0.5
pdensity <- function(x) wt * dnorm(x, 0, sd1) + (1 - wt) * dnorm(x, 0, sd2)
x <- seq(-3, 3, length = 200)

simseq <- function(N, prior.mu = 0, prior.sd, wt, mucut = 0, mucutf = 0.05,
                   postcut = 0.95, postcutf = 0.9, ignore = 20, nsim = 1000){
  prior.mu <- rep(prior.mu, length = 2)
  prior.sd <- rep(prior.sd, length = 2)
  sd1 <- prior.sd[1]; sd2 <- prior.sd[2]
  v1 <- sd1 ^ 2
  v2 <- sd2 ^ 2
  j <- 1 : N
  cmean <- Mu <- PostN <- Post <- Postf <- postfe <- postmean <- numeric(nsim)
  stopped <- stoppedi <- stoppedf <- stoppedfu <- stopfe <- status <- integer(nsim)
  notignored <- - (1 : ignore) # Problem here, this will be the last several data, not
                               # the ignore+1 : end
  pmean <- gbayesMixPost(NA, NA, d0 = prior.mu[1], d1 = prior.mu[2],
                         v0 = v1, v1 = v2, mix = wt, what = 'postmean')
  
  for(i in 1:nsim){
    component <- if(wt == 1) 1 else sample(1:2, size = 1, prob=c(wt, 1.-wt))
    mu <- prior.mu[component] + rnorm(1) * prior.sd[component]
    
    Mu[i] <- mu
    y <- rnorm(N, mean = mu, sd = 1)
    ybar <- cumsum(y) / j
    pcdf <- gbayesMixPost(ybar, 1. / j, d0 = prior.mu[1], d1 = prior.mu[2],
                          v0 = v1, v1 = v2, mix = wt, what = 'cdf')
    post <- 1 - pcdf(mucut)
    PostN[i] <- post[N]
    postf <- pcdf(mucutf)
    s <- stopped[i] <- if(max(post) < postcut) N else min(which(post >= postcut))
    Post[i] <- post[s]
    cmean[i] <- ybar[s]
    
    postmean[i] <- pmean(x = ybar[s], v = 1./s)
    
    stoppedi[i] <- if(max(post[notignored]) < postcut) N
    else
      ignore + min(which(post[notignored] >= postcut))
    
    stoppedf[i] <- if(max(post) < postcut & max(postf) < postcutf) N
    else
      min(which(post >= postcut | postf >= postcutf))
    
    s <- if(max(postf) < postcutf) N else min(which(postf >= postcutf))
    Postf[i] <- postf[s]
    stoppedfu[i] <- s
    
    stp <- post >= postcut | postf >= postcutf
    s <- stopfe[i] <- if(any(stp)) min(which(stp)) else N
    status[i] <- if(any(stp)) ifelse(postf[s] >= postcutf, 1, 2) else 0
    postfe[i] <- if(any(stp)) ifelse(status[i] == 2, post[s], postf[s]) else post[N]
  }
  list(mu = Mu, post = Post, postn = PostN, postf = Postf, stopped = stopped,
       stoppedi = stoppedi, stoppedf = stoppedf, stoppedfu = stoppedfu, 
       cmean = cmean, postmean = postmean, postfe = postfe, status = status,
       stopfe = stopfe)
}

set.seed(1)
z <- simseq(500, prior.mu = 0, prior.sd = c(sd1, sd2), wt = wt, postcut = 0.95,
            postcutf = 0.9, nsim = 100000)
mu <- z$mu
post <- z$post
postn <- z$postn
st <- z$stopped
sti <- z$stoppedi
stf <- z$stoppedf
stfu <- z$stoppedfu
cmean <- z$cmean
postmean <- z$postmean
postf <- z$postf
status <- z$status
postfe <- z$postfe
rmean <- function(x) formatNP(mean(x), digits = 3)
k <- status == 2
kf <- status == 1

# Trials stopped early for efficacy
print(sum(k))
# Trails stopped early for futility
print(sum(kf))
# Average post prob. of efficacy at stopping for efficacy:
print(mean(postfe[k]))
# Of trails stopped early for efficacy, proportion with mu > 0
print(sum((mu[status == 2] > 0))/sum(k))
# Average post prob. of futility at stopping for futility:
print(mean(postf[kf]))
# Of trails stopped early for futility, proportion with mu < 0.05
print(sum((mu[status == 1] < 0.05))/sum(kf))
```

## Code for research

### Final Bayesian Code (after Friday OH)

```{r}
library(tidyverse)

wt <- 0.3

sample_ve <- function(N, wt){
  sampled_ve_list = rep(NA, N)
  for(i in 1:N){
    if(runif(1) < wt){
      # sample from the first part
      X <- rbeta(1,2,1)
      sampled_ve_list[i] = 0.5*X
    }else{
      X <- rbeta(1,3,2)
      sampled_ve_list[i] = 1-0.5*X
    }
  }
  return(sampled_ve_list)
}

simseq <- function(N, chortsize, wt, vecut = 0.5, vecutf = 0.3, 
                   postcut = 0.95, postcutf = 0.95, 
                   nsim_trail = 1000, nsim_sim = 1000){
  
  postf <- postfe <- numeric(nsim_trail)
  stopped <- status <- integer(nsim_trail)
  ee <- ef <- ei <- fe <- ff <- fi <- ie <- i_f <- ii <- rep(0, nsim_trail)
  
  # generate the probabilities for nsim trials
  p2 <- rbeta(nsim_trail, 354, 34245)
  VE <- sample_ve(nsim_trail, wt)
  p1 <- p2*(1-VE)
  
  # Running through the simulated clinical trials
  for(i in 1:nsim_trail){
    # generate the data from a trial, 0 means uninfected, 1 means infected
    y_placebo <- rbinom(N, 1, p2[i])
    y_treat <- rbinom(N, 1, p1[i])
    
    # By cohort
    # Status: 0 no decision, 1 futility, 2 efficacious
    for(j in 1:ceiling(N/chortsize)){
      N_j <- j*chortsize
      y_p <- y_placebo[1:N_j]
      y_t <- y_treat[1:N_j]
      # Posterior
      post_p <- rbeta(nsim_sim, sum(y_p)+1, N_j-sum(y_p)+1)
      post_t <- rbeta(nsim_sim, sum(y_t)+1, N_j-sum(y_t)+1)
      post_VE <- rep(1, nsim_sim) - (post_t / post_p)
      # Efficacy, stop if Pr(VE(n) > vecut|data) > postcut
      post_VE_cutprob <- sum(post_VE > vecut) / nsim_sim
      if(post_VE_cutprob > postcut){
        # Stop the trial and record the values
        stopped[i] <- N_j
        status[i] <- 2
        postfe[i] <- mean(post_VE)
        break
      }
      # Futility, stop if Pr(VE(n) < vecutf|data) > postcutf
      post_VE_cutfprob <- sum(post_VE < vecutf) / nsim_sim
      if(post_VE_cutfprob > postcutf){
        # Stop the trial and record the values
        stopped[i] <- N_j
        status[i] <- 1
        postf[i] <- mean(post_VE)
        break
      }
      # Reach the end
      if(N_j == N){
        # This is the undermined case
        status[i] <- 0
        stopped[i] <- N
      }
    }
    
    # signal true approval, false approval and false refusal
    # the true status
    true_status <- 0
    if(VE[i] > 0.5) true_status = 2 
    else if(VE[i] < 0.3) true_status = 1
    # the estimated status
    est_status = status[i]
    
    
    # Estimate\Truth  | Effi  | Futi  | inconslusive
    #----------------------------------------
    #    Effi         |  ee   |  ef   |  ei
    #----------------------------------------
    #    Futi         |  fe   |  ff   |  fi
    #----------------------------------------
    #   inconslusive  |  ie   |  i_f  |  ii
    
    if(true_status == est_status && est_status == 0){
      ii[i] <- 1
    }else if(true_status == est_status && est_status == 1){
      ff[i] <- 1
    }else if(true_status == est_status && est_status == 2){
      ee[i] <- 1
    }else if(true_status == 0 && est_status == 1){
      fi[i] <- 1
    }else if(true_status == 0 && est_status == 2){
      ei[i] <- 1
    }else if(true_status == 1 && est_status == 0){
      i_f[i] <- 1
    }else if(true_status == 1 && est_status == 2){
      ef[i] <- 1
    }else if(true_status == 2 && est_status == 0){
      ie[i] <- 1
    }else if(true_status == 2 && est_status == 1){
      fe[i] <- 1
    }
    
  }
  
  list(postf = postf, postfe = postfe, stopped = stopped,
       status = status, truth = true_status, 
       ee = sum(ee), ef = sum(ef), ei = sum(ei),
       fe = sum(fe), ff = sum(ff), fi = sum(fi), 
       ie = sum(ie), i_f = sum(i_f), ii = sum(ii))
        
}

z <- simseq(18000, 3000, 0.3, nsim_trail = 10000)

# Print 3 by 3 table
three_by_three_table <- tibble(
  E_T = c("Effi", "Futi", "Inc"),
  Effi = c(z$ee, z$fe, z$ie),
  Futi = c(z$ef, z$ff, z$i_f),
  Inc = c(z$ei, z$fi, z$ii)
)
print(three_by_three_table)

# FAR: false approval rate
#             number of false approval                    ef + ei
# -------------------------------------------------- = --------------
# number of false approval + number of true approval   ef + ei + ee
FAR <- (z$ef + z$ei)/(z$ef + z$ei + z$ee)
print(paste("The FAR is:", FAR))

# TAR: true approval rate
#             number of true approval                       ee
# -------------------------------------------------- = --------------
# number of true approval + number of false approval   ef + ei + ee
TAR <- z$ee/(z$ef + z$ei + z$ee)
print(paste("The TAR is:", TAR))

# FRR: false refusal rate
#             number of false refusal                    fe + fi
# -------------------------------------------------- = --------------
# number of false refusal + number of true refusal     fe + ff + fi
FRR <- (z$fe + z$fi)/(z$fe + z$ff + z$fi)
print(paste("The FRR is:", FRR))

# Null: VE < 0.3

# Estimate\Truth       | Effi + inc (False) | Futi (True) 
#------------------------------------------------------------
#    Effi + inc (Rej)  |  ee + ei + ie + ii |  ef + i_f 
#------------------------------------------------------------
#    Futi (Fail Rej)   |  fe + fi           |  ff   

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (ef + i_f) / (ef + i_f + ff)

typeI <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
print(paste("The Type I error under the null of VE < 0.3 is:", typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (fe + fi) / (fe + fi + ee + ei + ie + ii)

typeII <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
print(paste("The Type II error under the null of VE < 0.3 is:", typeII))

# Bayesian Type I and Type II

# Estimate\Truth  | Effi  | Futi  | inconslusive
#----------------------------------------
#    Effi         |  ee   |  ef   |  ei
#----------------------------------------
#    Futi         |  fe   |  ff   |  fi
#----------------------------------------
#   inconslusive  |  ie   |  i_f  |  ii

# Null: VE >= 0.3
# Estimate\Truth       | Effi + inc (True) | Futi (False) 
#------------------------------------------------------------
# Effi + inc (Fail Rej)|  ee + ei + ie + ii |  ef + i_f 
#------------------------------------------------------------
#    Futi (Rej)        |  fe + fi           |  ff  

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (fe + fi) / (fe + fi + ee + ei + ie + ii)

bayes_fu_typeI <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
print(paste("The Type I error under the null of VE >= 0.3 is:", bayes_fu_typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (ef + i_f) / (ef + i_f + ff)

bayes_fu_typeII <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
print(paste("The Type II error under the null of VE >= 0.3 is:", bayes_fu_typeII))

# Null: VE <= 0.5
# Estimate\Truth       | Futi + inc (True)   | Effi (False) 
#------------------------------------------------------------
# Futi + inc (Fail Rej)|  ff + fi + i_f + ii |  fe + ie 
#------------------------------------------------------------
#    Effi (Rej)        |  ef + ei            |  ee  

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (ef + ei) / (ef + ei + ff + fi + i_f + ii)

bayes_eff_typeI <- (z$ef + z$ei)/(z$ef + z$ei + z$ff + z$fi + z$i_f + z$ii)
print(paste("The Type I error under the null of VE <= 0.5 is:", bayes_eff_typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (fe + ie) / (fe + ie + ee)

bayes_eff_typeII <- (z$fe + z$ie)/(z$fe + z$ie + z$ee)
print(paste("The Type II error under the null of VE <= 0.5 is:", bayes_eff_typeII))


status <- z$status
k <- z$status == 2 & z$stopped < 18000
kf <- z$status == 1 & z$stopped < 18000

# Trials stopped early for efficacy
print(paste("The number of trials with early stopping for efficacy is:", sum(k)))
# Trails stopped early for futility
print(paste("The number of trials with early stopping for futility is:", sum(kf)))
# Average post prob. of efficacy at stopping for efficacy:
#print(paste("The avg post efficacy at early stopping for efficacy is:", mean(z$postfe[k])))
# Average post prob. of futility at stopping for futility:
#print(paste("The avg post futility at early stopping for futility is:", mean(z$postf[kf])))

# Print early stopping for each interim
print("The stopping number of each interim:")
print(sum(z$stopped == 3000))
print(sum(z$stopped == 6000))
print(sum(z$stopped == 9000))
print(sum(z$stopped == 12000))
print(sum(z$stopped == 15000))
print(sum(z$stopped == 18000))

# Average stopping time
print(paste("Average stopping sample size", mean(z$stopped)))

# Print early stopping for each interim for different status
# Stop for futility
print("The stopping number of each interim for futility:")
print(sum(z$stopped == 3000 & z$status == 1))
print(sum(z$stopped == 6000 & z$status == 1))
print(sum(z$stopped == 9000 & z$status == 1))
print(sum(z$stopped == 12000 & z$status == 1))
print(sum(z$stopped == 15000 & z$status == 1))
print(sum(z$stopped == 18000 & z$status == 1))

print(paste("Average stopping sample size for futility early stopping", mean(z$stopped[kf])))
# Stop for efficicous
print("The stopping number of each interim for efficacy:")
print(sum(z$stopped == 3000 & z$status == 2))
print(sum(z$stopped == 6000 & z$status == 2))
print(sum(z$stopped == 9000 & z$status == 2))
print(sum(z$stopped == 12000 & z$status == 2))
print(sum(z$stopped == 15000 & z$status == 2))
print(sum(z$stopped == 18000 & z$status == 2))

print(paste("Average stopping sample size for efficacy early stopping", mean(z$stopped[k])))

# Overall accuracy
# print(sum(z$truth - z$status)/10000)
```

### test of cut = 0.3

```{r}
zz <- simseq(18000, 3000, 0.3, vecut = 0.3, nsim_trail = 10000)

# Print 3 by 3 table
three_by_three_table2 <- tibble(
  E_T = c("Effi", "Futi", "Inc"),
  Effi = c(zz$ee, zz$fe, zz$ie),
  Futi = c(zz$ef, zz$ff, zz$i_f),
  Inc = c(zz$ei, zz$fi, zz$ii)
)
print(three_by_three_table2)

```


### Simulation on weight

```{r}
library(ggplot2)
library(tidyverse)


# simulate various values of wt
#wt_list <- c(0.01, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
wt_list <- seq(0.03,1,by=0.03)

far_wt_list <- tar_wt_list <- frr_wt_list <- rep(NA, length(wt_list))
typeI_wt <- typeII_wt <- rep(NA, length(wt_list))
trial_eff_wt <- trial_fu_wt <- rep(NA, length(wt_list))
ave_patient_number_eff_wt <- ave_patient_number_fu_wt <- rep(NA, length(wt_list))

for(idx in 1:length(wt_list)){
  wt <- wt_list[idx]
  z <- simseq(18000, 3000, wt, nsim_trail = 1000)
  far_wt_list[idx] <- (z$ef + z$ei)/(z$ef + z$ei + z$ee)
  tar_wt_list[idx] <- z$ee/(z$ef + z$ei + z$ee)
  frr_wt_list[idx] <- (z$fe + z$fi)/(z$fe + z$ff + z$fi)
  typeI_wt[idx] <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
  typeII_wt[idx] <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
  
  
  status <- z$status
  k <- z$status == 2
  kf <- z$status == 1
  
  trial_eff_wt[idx] <- sum(k)
  trial_fu_wt[idx] <- sum(kf)
  
  kk <- z$status == 2 & z$stopped < 18000
  kkf <- z$status == 1 & z$stopped < 18000
  
  ave_patient_number_eff_wt[idx] <- mean(z$stopped[kk])
  ave_patient_number_fu_wt[idx] <- mean(z$stopped[kkf])
}

data_rate <- data.frame(wt = wt_list, far = far_wt_list, tar = tar_wt_list, frr = frr_wt_list)
plot_data_rate <- data_rate %>%
  pivot_longer(cols = c('far', 'tar', 'frr'), names_to = "rate", values_to = "values")

data_type_err <- data.frame(wt = wt_list, typeI = typeI_wt, typeII = typeII_wt)
plot_data_err <- data_type_err %>%
  pivot_longer(cols = c('typeI', 'typeII'), 
               names_to = "error", values_to = "values")

data_stop <- data.frame(wt = wt_list, efficacy = trial_eff_wt, futility = trial_fu_wt)
plot_data_stop <- data_stop %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "stop", values_to = "values")

data_patient <- data.frame(wt = wt_list, efficacy = ave_patient_number_eff_wt, futility = ave_patient_number_fu_wt)
plot_data_patient <- data_patient %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "patient", values_to = "values")

ggplot(data = plot_data_rate, aes(x = wt, y = values, col = rate)) + 
  geom_line() +
  xlab("Weight") + ylab("Error Rate")

ggplot(data = plot_data_err, aes(x = wt, y = values, col = error)) + 
  geom_line() +
  xlab("Weight") + ylab("Type I and II errors")

ggplot(data = plot_data_stop, aes(x = wt, y = values, col = stop)) + 
  geom_line() +
  xlab("Weight") + ylab("Stopped Number")

ggplot(data = plot_data_patient, aes(x = wt, y = values, col = patient)) + 
  geom_line() +
  xlab("Weight") + ylab("Average Patient Number")
```

### Simulation on efficacy cutoff

```{r}
# simulate various values of wt
#eff_cut_list <- c(0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96, 0.97, 0.98, 0.99)
eff_cut_list <- seq(0.7,1,by = 0.005)

far_wt_list <- tar_wt_list <- frr_wt_list <- rep(NA, length(eff_cut_list))
typeI_wt <- typeII_wt <- rep(NA, length(eff_cut_list))
trial_eff_wt <- trial_fu_wt <- rep(NA, length(eff_cut_list))
ave_patient_number_eff_wt <- ave_patient_number_fu_wt <- rep(NA, length(eff_cut_list))

for(idx in 1:length(eff_cut_list)){
  pcut <- eff_cut_list[idx]
  z <- simseq(18000, 3000, 0.3, nsim_trail = 1000, postcut = pcut)
  far_wt_list[idx] <- (z$ef + z$ei)/(z$ef + z$ei + z$ee)
  tar_wt_list[idx] <- z$ee/(z$ef + z$ei + z$ee)
  frr_wt_list[idx] <- (z$fe + z$fi)/(z$fe + z$ff + z$fi)
  typeI_wt[idx] <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
  typeII_wt[idx] <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
  
  status <- z$status
  k <- z$status == 2
  kf <- z$status == 1
  
  trial_eff_wt[idx] <- sum(k)
  trial_fu_wt[idx] <- sum(kf)
  
  kk <- z$status == 2 & z$stopped < 18000
  kkf <- z$status == 1 & z$stopped < 18000
  
  ave_patient_number_eff_wt[idx] <- mean(z$stopped[kk])
  ave_patient_number_fu_wt[idx] <- mean(z$stopped[kkf])
}

data_rate <- data.frame(wt = eff_cut_list, far = far_wt_list, tar = tar_wt_list, frr = frr_wt_list)
plot_data_rate <- data_rate %>%
  pivot_longer(cols = c('far', 'tar', 'frr'), names_to = "rate", values_to = "values")

data_type_err <- data.frame(wt = eff_cut_list, typeI = typeI_wt, typeII = typeII_wt)
plot_data_err <- data_type_err %>%
  pivot_longer(cols = c('typeI', 'typeII'), 
               names_to = "error", values_to = "values")

data_stop <- data.frame(wt = eff_cut_list, efficacy = trial_eff_wt, futility = trial_fu_wt)
plot_data_stop <- data_stop %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "stop", values_to = "values")

data_patient <- data.frame(wt = eff_cut_list, efficacy = ave_patient_number_eff_wt, futility = ave_patient_number_fu_wt)
plot_data_patient <- data_patient %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "patient", values_to = "values")

ggplot(data = plot_data_rate, aes(x = wt, y = values, col = rate)) + 
  geom_line() +
  xlab("Efficacy Posterior Cutoff Probability") + ylab("Error Rate")

ggplot(data = plot_data_err, aes(x = wt, y = values, col = error)) + 
  geom_line() +
  xlab("Efficacy Posterior Cutoff Probability") + ylab("Type I and II errors")

ggplot(data = plot_data_stop, aes(x = wt, y = values, col = stop)) + 
  geom_line() +
  xlab("Efficacy Posterior Cutoff Probability") + ylab("Stopped Number")

ggplot(data = plot_data_patient, aes(x = wt, y = values, col = patient)) + 
  geom_line() +
  xlab("Efficacy Posterior Cutoff Probability") + ylab("Average Patient Number")

```

### Simulation on futility cutoff

```{r}
# simulate various values of wt
#fu_cut_list <- c(0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96, 0.97, 0.98, 0.99)
fu_cut_list <- seq(0.7,1,by = 0.005)

far_wt_list <- tar_wt_list <- frr_wt_list <- rep(NA, length(fu_cut_list))
typeI_wt <- typeII_wt <- rep(NA, length(fu_cut_list))
trial_eff_wt <- trial_fu_wt <- rep(NA, length(fu_cut_list))
ave_patient_number_eff_wt <- ave_patient_number_fu_wt <- rep(NA, length(fu_cut_list))

for(idx in 1:length(fu_cut_list)){
  pcutf <- fu_cut_list[idx]
  z <- simseq(18000, 3000, 0.3, nsim_trail = 1000, postcutf = pcutf)
  far_wt_list[idx] <- (z$ef + z$ei)/(z$ef + z$ei + z$ee)
  tar_wt_list[idx] <- z$ee/(z$ef + z$ei + z$ee)
  frr_wt_list[idx] <- (z$fe + z$fi)/(z$fe + z$ff + z$fi)
  typeI_wt[idx] <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
  typeII_wt[idx] <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
  
  status <- z$status
  k <- z$status == 2
  kf <- z$status == 1
  
  trial_eff_wt[idx] <- sum(k)
  trial_fu_wt[idx] <- sum(kf)
  
  kk <- z$status == 2 & z$stopped < 18000
  kkf <- z$status == 1 & z$stopped < 18000
  
  ave_patient_number_eff_wt[idx] <- mean(z$stopped[kk])
  ave_patient_number_fu_wt[idx] <- mean(z$stopped[kkf])
}

data_rate <- data.frame(wt = fu_cut_list, far = far_wt_list, tar = tar_wt_list, frr = frr_wt_list)
plot_data_rate <- data_rate %>%
  pivot_longer(cols = c('far', 'tar', 'frr'), names_to = "rate", values_to = "values")

data_type_err <- data.frame(wt = fu_cut_list, typeI = typeI_wt, typeII = typeII_wt)
plot_data_err <- data_type_err %>%
  pivot_longer(cols = c('typeI', 'typeII'), 
               names_to = "error", values_to = "values")

data_stop <- data.frame(wt = fu_cut_list, efficacy = trial_eff_wt, futility = trial_fu_wt)
plot_data_stop <- data_stop %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "stop", values_to = "values")

data_patient <- data.frame(wt = fu_cut_list, efficacy = ave_patient_number_eff_wt, futility = ave_patient_number_fu_wt)
plot_data_patient <- data_patient %>%
  pivot_longer(cols = c('efficacy', 'futility'), 
               names_to = "patient", values_to = "values")

ggplot(data = plot_data_rate, aes(x = wt, y = values, col = rate)) + 
  geom_line() +
  xlab("Futility Posterior Cutoff Probability") + ylab("Error Rate")

ggplot(data = plot_data_err, aes(x = wt, y = values, col = error)) + 
  geom_line() +
  xlab("Futility Posterior Cutoff Probability") + ylab("Type I and II errors")

ggplot(data = plot_data_stop, aes(x = wt, y = values, col = stop)) + 
  geom_line() +
  xlab("Futility Posterior Cutoff Probability") + ylab("Stopped Number")

ggplot(data = plot_data_patient, aes(x = wt, y = values, col = patient)) + 
  geom_line() +
  xlab("Futility Posterior Cutoff Probability") + ylab("Average Patient Number")

```
Here again we use the same method as before, but with hyper parameters.
Since we are dealing with Covid-19 vaccine, then we would prefer the parameters
that give lower frr, so we would have higher chance to approve effective
vaccines. On the other hand, we would also like to use less patients to do
the test due to ethic reasons, because we don't want people to inject
futile vaccine. Also, less patients needed to complete the test means time
and money can be saved.

Lets use wt = 0.2, postcut = 0.85, postcutf = 0.98 
```{r}
z <- simseq(18000, 3000, wt = 0.2,postcut = 0.85, postcutf = 0.98, nsim_trail = 10000)

# Print 3 by 3 table
three_by_three_table <- tibble(
  E_T = c("Effi", "Futi", "Inc"),
  Effi = c(z$ee, z$fe, z$ie),
  Futi = c(z$ef, z$ff, z$i_f),
  Inc = c(z$ei, z$fi, z$ii)
)
print(three_by_three_table)

# FAR: false approval rate
#             number of false approval                    ef + ei
# -------------------------------------------------- = --------------
# number of false approval + number of true approval   ef + ei + ee
FAR <- (z$ef + z$ei)/(z$ef + z$ei + z$ee)
print(paste("The FAR is:", FAR))

# TAR: true approval rate
#             number of true approval                       ee
# -------------------------------------------------- = --------------
# number of true approval + number of false approval   ef + ei + ee
TAR <- z$ee/(z$ef + z$ei + z$ee)
print(paste("The TAR is:", TAR))

# FRR: false refusal rate
#             number of false refusal                    fe + fi
# -------------------------------------------------- = --------------
# number of false refusal + number of true refusal     fe + ff + fi
FRR <- (z$fe + z$fi)/(z$fe + z$ff + z$fi)
print(paste("The FRR is:", FRR))

# Null: VE < 0.3

# Estimate\Truth       | Effi + inc (False) | Futi (True) 
#------------------------------------------------------------
#    Effi + inc (Rej)  |  ee + ei + ie + ii |  ef + i_f 
#------------------------------------------------------------
#    Futi (Fail Rej)   |  fe + fi           |  ff   

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (ef + i_f) / (ef + i_f + ff)

typeI <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
print(paste("The Type I error under the null of VE < 0.3 is:", typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (fe + fi) / (fe + fi + ee + ei + ie + ii)

typeII <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
print(paste("The Type II error under the null of VE < 0.3 is:", typeII))

# Bayesian Type I and Type II

# Estimate\Truth  | Effi  | Futi  | inconslusive
#----------------------------------------
#    Effi         |  ee   |  ef   |  ei
#----------------------------------------
#    Futi         |  fe   |  ff   |  fi
#----------------------------------------
#   inconslusive  |  ie   |  i_f  |  ii

# Null: VE >= 0.3
# Estimate\Truth       | Effi + inc (True) | Futi (False) 
#------------------------------------------------------------
# Effi + inc (Fail Rej)|  ee + ei + ie + ii |  ef + i_f 
#------------------------------------------------------------
#    Futi (Rej)        |  fe + fi           |  ff  

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (fe + fi) / (fe + fi + ee + ei + ie + ii)

bayes_fu_typeI <- (z$fe + z$fi)/(z$fe + z$fi + z$ee + z$ei + z$ie + z$ii)
print(paste("The Type I error under the null of VE >= 0.3 is:", bayes_fu_typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (ef + i_f) / (ef + i_f + ff)

bayes_fu_typeII <- (z$ef + z$i_f)/(z$ef + z$i_f + z$ff)
print(paste("The Type II error under the null of VE >= 0.3 is:", bayes_fu_typeII))

# Null: VE <= 0.5
# Estimate\Truth       | Futi + inc (True)   | Effi (False) 
#------------------------------------------------------------
# Futi + inc (Fail Rej)|  ff + fi + i_f + ii |  fe + ie 
#------------------------------------------------------------
#    Effi (Rej)        |  ef + ei            |  ee  

# Type I error = Dec Rej & Null true / (Dec Rej & Null true + Dec Fail Rej & Null True)
#              = (ef + ei) / (ef + ei + ff + fi + i_f + ii)

bayes_eff_typeI <- (z$ef + z$ei)/(z$ef + z$ei + z$ff + z$fi + z$i_f + z$ii)
print(paste("The Type I error under the null of VE <= 0.5 is:", bayes_eff_typeI))

# Type II error = Dec fail Rej & Null false / (Dec fail Rej & Null false + Dec Rej & Null false)
#               = (fe + ie) / (fe + ie + ee)

bayes_eff_typeII <- (z$fe + z$ie)/(z$fe + z$ie + z$ee)
print(paste("The Type II error under the null of VE <= 0.5 is:", bayes_eff_typeII))


status <- z$status
k <- z$status == 2 & z$stopped < 18000
kf <- z$status == 1 & z$stopped < 18000

# Trials stopped early for efficacy
print(paste("The number of trials with early stopping for efficacy is:", sum(k)))
# Trails stopped early for futility
print(paste("The number of trials with early stopping for futility is:", sum(kf)))
# Average post prob. of efficacy at stopping for efficacy:
#print(paste("The avg post efficacy at early stopping for efficacy is:", mean(z$postfe[k])))
# Average post prob. of futility at stopping for futility:
#print(paste("The avg post futility at early stopping for futility is:", mean(z$postf[kf])))

# Print early stopping for each interim
print("The stopping number of each interim:")
print(sum(z$stopped == 3000))
print(sum(z$stopped == 6000))
print(sum(z$stopped == 9000))
print(sum(z$stopped == 12000))
print(sum(z$stopped == 15000))
print(sum(z$stopped == 18000))

# Average stopping time
print(paste("Average stopping sample size", mean(z$stopped)))

# Print early stopping for each interim for different status
# Stop for futility
print("The stopping number of each interim for futility:")
print(sum(z$stopped == 3000 & z$status == 1))
print(sum(z$stopped == 6000 & z$status == 1))
print(sum(z$stopped == 9000 & z$status == 1))
print(sum(z$stopped == 12000 & z$status == 1))
print(sum(z$stopped == 15000 & z$status == 1))
print(sum(z$stopped == 18000 & z$status == 1))

print(paste("Average stopping sample size for futility early stopping", mean(z$stopped[kf])))
# Stop for efficicous
print("The stopping number of each interim for efficacy:")
print(sum(z$stopped == 3000 & z$status == 2))
print(sum(z$stopped == 6000 & z$status == 2))
print(sum(z$stopped == 9000 & z$status == 2))
print(sum(z$stopped == 12000 & z$status == 2))
print(sum(z$stopped == 15000 & z$status == 2))
print(sum(z$stopped == 18000 & z$status == 2))

print(paste("Average stopping sample size for efficacy early stopping", mean(z$stopped[k])))

# Overall accuracy
# print(sum(z$truth - z$status)/10000)
```
```
